### 2009-03-02 doc/ws-programming-tutorial/doc/tex_appendix/appendix.tex
Checked the whole document up to the Sec Echo Web Service. Started writting more about the Sec Echo Web Service. Added XSD of the XML configuration file to the appendix.

\section{Important XSD files}

>>>>

Questions:
\begin{itemize}
 \item The images of the HED structure always are ordered like: TCP - TLS - HTTP - PLEXER - SOAP - Web Service   but the source code examples are: TCP - TLS - HTTP - SOAP - PLEXER - Web Service
 \item Does HED realises a replication Server which delegates incoming request to several threads which are communicating to the client on other free ports (I guess that not). i.e.  Front end server is running on port 60000. Request will be delegated to thread which creates a new socket on port 54305. The communication get delegated and the front end is ready for new requests.
\end{itemize}

\section{Important XSD files}
\lstsetJUSTXML
\lstinputlisting
	[
	label=lst:arched_arcecho_xml,
	caption={[HED configuration. Filename: arcecho\_no\_ssl.xml]
	\textbf{HED configuration. Filename: arcecho\_no\_ssl.xml\textcolor{white}{hmf}}}
	]
{../../../src/hed/libs/loader/mcc.xsd}

\task{RENAMING HED configuration file into~ARC service configuration file - proposed by Marek}
\task{(echo service) client configuration file - proposed by Marek}

### 2009-03-02 doc/ws-programming-tutorial/doc/tex_echoservice/echoservice.tex
Checked the whole document up to the Sec Echo Web Service. Started writting more about the Sec Echo Web Service. Added XSD of the XML configuration file to the appendix.

\chapter{The echo service}

The next service to be presented is the echo service.
Its task is to return the content of the received message back to the client.
Furthermore, the service provides two additional operations called ``ordinary'' and ``reverse''.
Depending on the operation chosen by the client, the message will returned unmodified or it is shown with its reversed.
The goal of this chapter is to offer a deeper knowledge about message processing.
Also, the \textit{WSDL} (Web Services Description Language) will be introduced, with which the section now starts.

@@

Web services can be specified (not implemented) by a meta language called \textit{WSDL} (Web Services Description Language). 
Beside the description of the service, WSDL renders the possibility that services can be discovered by service brokers.
The discovery of services may be useful for an automatic adaption of a running client, i.e. if the endpoint of the service changes or to share the load of demands.
The WSDL service specification enables the programmer to implement a suitable client which interfaces the service in a proper way.
WSDL describes the structure of the messages, the intended use of the messages, the supported protocols and the endpoint of the service (URL).
For that last reason, every instance of a service must be produced a distinct WSDL file for - or - it is automatically prepared from the information that the server has available once it is implemented.

The WSDL file that specifies the here presented echo service is shown in listing~\ref{lst:echo_wsdl}. 
It is composed of five main elements:
\newcommand{\parboxWidth}{13cm}
\begin{itemize}
	\item \textbf{Types} --- The element \textit{types} contains the description of the message structures and is written in the language XSD (XML Schema Definition). The data types used for the messages of the echo service are defined starting with the  line~\ref{lst_code:echo_wsdl_types}.

	\item \textbf{Message} --- Within the element \textit{message} a subset of the previously defined types are assigned to be a message. In case of the echo service two messages are designated: echoRequest and echoResponse, compare lines line~\ref{lst_code:echo_wsdl_message1} and \ref{lst_code:echo_wsdl_message2}.

@@

	\item \textbf{Service} --- Within the last WSDL element \textit{service} the endpoint of the service gets specified. As to be seen in line~\ref{lst_code:echo_wsdl_service} the endpoint of the echo service is assigned to \textit{http://localhost:60000/echo}.

@@

The optional SOAP Fault element is used to indicate error messages.
If a \textit{Fault} element is present, it must appear as a child element of the \textit{Body} element. A \textit{Fault} element can only appear once in a SOAP message.

@@

\task{Source of the above two tables?}

@@

This section presents the implementation of the service defined in the WSDL file of the previous section.
The source code of the C++ file is shown in listing~\ref{lst:echo_service_cpp}.
Again, the header file will be set aside for it contains only redundant information.
It can be reread in the source directory that is accompanying the tutorial.
For the source code of echo service basically three changes are required for on the code for the timeservice webservice of the previous chapter.
The first change concerns the constructor and is found at line~\ref{lst_code:echo_cpp_prefix}.
Two strings will be extracted of the HED configuration file which are later used to envelope the message before it is returned.
Furthermore, a new method \textit{makeFault} in line~\ref{lst_code:echo_cpp_makeFault} has been introduced which is able to create fault messages and is called by the method \textit{process}.
Within that method two new code fragments are now extracting and analyzing the incoming message, to be seen at lines~\ref{lst_code:echo_cpp_extracting} and \ref{lst_code:echo_cpp_analyzing}.
In case something unexpected happens both will create a SOAP fault message.\\
% Vielleicht noch etwas über das extrahieren der Nachricht schreiben

@@

Again, the HED is configured by an XML file and is launched as introduced earlier.
The HED configuration file is shown in Listing~\ref{lst:echo_hed_configuration_xml}.
The only change concerns the lines~\ref{lst_code:echo_hed_configuration_xml_pre} and \ref{lst_code:echo_hed_configuration_xml_pre} which specify the \textit{prefix} and \textit{suffix}.
The parameters will be extracted in the constructor of the service and explain nicely how settings can be passed from the HED configuration file towards the service.

\lstsetARCHEDXML
\lstinputlisting
	[
	label=lst:echo_hed_configuration_xml, float=htb,
	caption={[HED configuration file for the echo service. Filename: arched\_echoservice.xml]
	\textbf{HED configuration file for the echo service. Filename: arched\_echoservice.xml}}
	]
{../src/services/echoservice/arched_echoservice.xml}

@@

With the interface of the server gaining complexity, so is the code for the client - for two reasons. Firstly, because the additional arguments need to be filled. Secondly, because of the extra effort to interact with the (here human) user to collect the data to forward to the echo service.
The parameters are now passed by the command line, to be seen in the lines followed by line~\ref{lst_code:echo_client_cpp_arguments}.
That code is independent from the ARC library.
The creation of the SOAP client is unchanged.
The request is created in lines subsequent line~\ref{lst_code:echo_client_cpp_request}.
It is processed in the code after line~\ref{lst_code:echo_client_cpp_response} in which also the response is received.
The checks of the response have expanded by an additional condition which tests for a fault message, see line~\ref{lst_code:echo_client_cpp_fault}.

@@

The usage of the client is presented in Listing~\ref{lst:invokation_echoservice}.
Three cases of echo service responses are displayed: ordinary operation, reverse operation and SOAP fault due to an unknown operation.

@@

A few examples for the exchanged messages are shown in the Listings~\ref{lst:echoservice_request}, \ref{lst:echoservice_response} and \ref{lst:echoservice_fault}. Listing~\ref{lst:echoservice_request} illustrates a request message using the operation \textit{reverse}.
Listing~\ref{lst:echoservice_response} illustrates the corresponding response message. When the operation requested by the client is unknown, then the server replies with the fault message shown in Listing~\ref{lst:echoservice_fault}.

>>>>

\chapter{The Echo Web Service}

The next service to be presented is the Echo Web Service.
Its task is to return the content of the received message back to the client.
Furthermore, the service provides two additional operations called ``ordinary'' and ``reverse''.
Depending on the operation chosen by the client, the message gets returned unmodified or reversed.
The goal of this chapter is to offer a deeper knowledge about message processing.
Also, the \textit{WSDL} (Web Services Description Language) will be introduced, with which the section now starts.

@@

Web Services can be specified (not implemented) by a meta language called \textit{WSDL} (Web Services Description Language).
Beside the description of the service, WSDL renders the possibility that services can be discovered by service brokers.
The discovery of services may be useful for an automatic adaption of a running client, i.e. if the endpoint of the service changes or to share the load of demands.
The WSDL service specification enables the programmer to implement a suitable client which interfaces the service in a proper way.
WSDL describes the structure of the messages, the intended use of the messages, the supported protocols and the endpoint of the service (URL).
\task{For that last reason, every instance of a service must be produced a distinct WSDL file for - or - it is automatically prepared from the information that the server has available once it is implemented. - ?MG }\\

The WSDL file that specifies the here presented Echo Web Service is shown in listing~\ref{lst:echo_wsdl}. 
It is composed of five main elements:
\newcommand{\parboxWidth}{13cm}
\begin{itemize}
	\item \textbf{Types} --- The element \textit{types} contains the description of the message structures and is written in the language XSD (XML Schema Definition). The data types used for the messages of the Echo Web Service are defined starting with the  line~\ref{lst_code:echo_wsdl_types}.

	\item \textbf{Message} --- Within the element \textit{message} a subset of the previously defined types are assigned to be a message. In case of the Echo Web Service  two messages are designated: echoRequest and echoResponse, compare lines line~\ref{lst_code:echo_wsdl_message1} and \ref{lst_code:echo_wsdl_message2}.

@@

	\item \textbf{Service} --- Within the last WSDL element \textit{service} the endpoint of the service gets specified. As to be seen in line~\ref{lst_code:echo_wsdl_service} the endpoint of the Echo Web Service  is assigned to \textit{http://localhost:60000/echo}.

@@

The optional SOAP Fault element is used to indicate error messages in case of the port type \textit{solicit-response} (input, output, fault).
If a \textit{Fault} element is present, it must appear as a child element of the \textit{Body} element. A \textit{Fault} element can only appear once in a SOAP message.

@@

\task{Source of the above two tables? Extension of the second table? Numbers??}

@@

This section presents the implementation of the service defined in the WSDL file of the previous section.
The source code of the C++ file is shown in listing~\ref{lst:echo_service_cpp}.
The header file will be set aside for it contains only redundant information. 
It can be reread in the source directory that is accompanying the tutorial.
Regarding to the source code of the Echo Web Service basically three changes of the Time Web Service source code will be required.
The first change concerns the constructor and can be found at line~\ref{lst_code:echo_cpp_prefix}.
Two strings are extracted of the server configuration file which later are used to envelope the message before it is returned.
Furthermore, a new method \textit{makeFault} in line~\ref{lst_code:echo_cpp_makeFault} has been introduced which is able to create the fault messages and is called by the method \textit{process}.
Within the method \textit{process} two new code fragments are now extracting and analyzing the incoming message, to be seen at line~\ref{lst_code:echo_cpp_extracting} and \ref{lst_code:echo_cpp_analyzing}.
In case something unexpected happens both will create a SOAP fault message.\\
% Vielleicht noch etwas über das extrahieren der Nachricht schreiben

@@

Again, the HED is configured by an XML file and is launched as introduced earlier.
The server configuration file is shown in Listing~\ref{lst:echo_hed_configuration_xml}.
The only change concerns the lines~\ref{lst_code:echo_hed_configuration_xml_pre} and \ref{lst_code:echo_hed_configuration_xml_pre} which specify the \textit{prefix} and \textit{suffix}.
The parameters will be extracted in the constructor of the service and explain nicely how settings can be passed from the server configuration file towards the service.

\lstsetARCHEDXML
\lstinputlisting
	[
	label=lst:echo_hed_configuration_xml, float=htb,
	caption={[Server configuration file for the echo service. Filename: arched\_echoservice.xml]
	\textbf{Server configuration file for the echo service. Filename: arched\_echoservice.xml}}
	]
{../src/services/echoservice/arched_echoservice.xml}

@@

With the interface of the server gaining complexity, so is the code for the client - for two reasons. Firstly, because the additional arguments need to be filled. Secondly, because of the extra effort to interact with the (here human) user to collect the data to forward to the Echo Web Service.
The parameters are now passed by the command line, to be seen in the lines followed by line~\ref{lst_code:echo_client_cpp_arguments}.
That code is independent from the ARC library.
The creation of the SOAP client is unchanged and the request is created in the lines subsequent line~\ref{lst_code:echo_client_cpp_request}.
It is processed in the code after line~\ref{lst_code:echo_client_cpp_response} in which also the response is received.
The checks of the response have expanded by an additional condition which tests for a fault message, see line~\ref{lst_code:echo_client_cpp_fault}.

@@

The usage of the client is presented in Listing~\ref{lst:invokation_echoservice}.
Three cases of Echo Web Service responses are displayed: ordinary operation, reverse operation and SOAP fault due to an unknown operation.

@@

A few examples of exchanged messages are shown in the Listings~\ref{lst:echoservice_request}, \ref{lst:echoservice_response} and \ref{lst:echoservice_fault}. Listing~\ref{lst:echoservice_request} illustrates a request message using the operation \textit{reverse}.
Listing~\ref{lst:echoservice_response} illustrates the corresponding response message. When the operation requested by the client is unknown, then the server replies with the fault message shown in Listing~\ref{lst:echoservice_fault}.

### 2009-03-02 doc/ws-programming-tutorial/doc/tex_introduction/introduction.tex
Checked the whole document up to the Sec Echo Web Service. Started writting more about the Sec Echo Web Service. Added XSD of the XML configuration file to the appendix.

This document gently introduces to preparation of standalone webservices and cognate clients with the Advance Resource Connector (ARC).
The reader is guided through a series of the practically oriented examples.
Each are accompanied by explanations of the main concepts of the software architecture.
No particular skills are required to follow the presented steps.
It is however beneficial to have some basic comprehension of the programming language C++, the file format XML and any regular UNIX shell.
To start, the user shall have an installation of ARC-1, as it is performed with current RPM or .deb packages\footnote{see http://wiki.nordugrid.org for explicit instructions for your setup}.

@@

In general, the implementation of a client is easier than the implementation of the server. 
ARC is designed as a middleware which encapsulates typical challenges of server-client infrastructures (security, exception handling, extensibility) and abstracts from the underlying computer architecture (heterogeneity of computers, computer location, protocols).
The core of ARC is the prior mentioned HED (Hosting Environment Daemon).
To the administrator HED is mostly visible as the single binary that is started and configured by a file that describes services that shall be prepared by HED.
Conceptionally, the HED determines how services shall be organised both as a principle, and for any given ARC-run server.
HED determines the very explicit presence or absence of a service at a particular address. Its many configurable layers are described later in this tutorial. 
%
At the time of writing, the endpoint of the HED will be a SOAP based webservice.
SOAP is a long established XML-based standard for web service communication.
ARC abstracts from this format, but nevertheless it is useful to be aware of
the underlying message transport mechanism.

@@

The HED which was already mentioned in the section above. As an essential part of the ARC middleware it provides the hosting of various services at the application level.
Its modularity allows its dynamic extension.
Figure~\ref{fig:HED_internal} illustrates a typical setup of a server-sided HED.
The HED consists of a few compononents called Message Chain Components (MCC).
These are ordered within a layered structure and several \textcolor{urgent}{modules}, which shall aid the programmer to simplify the development of the web services: Config, Loader, Logging, XMLNode.

\begin{figure}[htb]
	\centering
	\includegraphics[width=14cm]{tex_introduction/HED.pdf}
	\mycaption{Example of HED structure with an Arex service and a file service.\task{ Replace image by an easier one!} }{\task{Write more stuff}\task{The images of the HED structure always are ordered like: TCP - TLS - HTTP - PLEXER - SOAP - WEB SERVICE   but the source code examples are: TCP - TLS - HTTP - SOAP - PLEXER - WEB SERVICE}}
\label{fig:HED_internal}
\end{figure}

The MCCs are passing the incoming and outgoing messages to the upper or the respective lower layer. \task{which means? SM}
The lowest layer has to be a transport protocol like TCP which enables the transmission between the two applications, the client and the server.
Technically, there are lower leves, e.g. the Internet Protocol (IP) enables the transmission between two computers and is a technical requirement for the TCP layer.
But IP is not directly modelled by the HED.
TCP is well suited for the application because it provides a reliable and ordered delivery of a byte stream which is important to ensure security.
Above the TCP layer is the Hypertext Transfer Protocol (HTTP). 
In case a security layer is desired for authentication, the TLS (Transport Layer Security formerly known as SSL, Secure Sockets Layer) is inserted between the TCP and HTTP layers.
The HTTP provides the client-server architecture. It is stateless but offers several extensions for requests, header information and status codes. Furthermore HTTP enables the usage of Uniform Resource Locators (URL) which is used by ARC to multiplex between different services. The multiplexing layer can also be defined within the HED and is called Plexer.
Depending on the path of the URL the Plexer passes messages to a defined SOAP service which again passes the message to the Web Service.

The structure of the HED can be configured freely by modifying the HED configuration file.
A first impression how the HED can be configured shall be given in the following example which corresponds to the HED shown in figure~\ref{fig:HED_internal}.
It uses the ARC echo service~\cite{QIANG_2005} that is shipped for testing purposes with the ARC source code.

@@

\task{Where is the xsd file for HED configuration files??}
The first example shall give a basic understanding in how to configure the HED for setting up a novel service.
Here, the task is to setup the regular ARC Echo Web Service.
On the command line, all that needs to be done is to invoking the \textit{arched}\footnote{read: arc-hed} daemon with a fitting HED configuration file.
An example is shown in Listing~\ref{lst:arched_arcecho_xml}.
It is written in XML and its structure is based on the \textcolor{urgent}{??} schema.

@@

\lstinputlisting
	[
	label=lst:arched_arcecho_xml,float,
	caption={[HED configuration. Filename: arcecho\_no\_ssl.xml]
	\textbf{HED configuration. Filename: arcecho\_no\_ssl.xml\textcolor{white}{hmf}}}
	]
{../src/services/arched_arcecho.xml}
The first line of the XML file contains the XML declaration.
Several attributes can be defined here but at least the XML version should be specified.
The configuration as a whole is encapsulated by the \textit{<ArcConfig>} tag. It also performs the setting of namespace abbreviations, which are expected to be mostly invariant across all server installations.
The \textit{Server} element, to be found at line~\ref{lst_code:arched_arcecho_Server}, provides basic settings for the daemon such as location of the Pid-file or the Log-file.
The \textit{ModuleManager} holds the path to the plugin libraries.
Several paths may be defined here.
Due to the fact that the first library fitting to the plugin name is loaded, the order is relevant.
The path should be at least assigned to the ARC installation directory.
Otherwise, the standard set of MCC modules might not be found.
The next set of elements are holding the name of the plugins to be loaded (line~\ref{lst_code:arched_arcecho_Plugins}).
The names have to correspond to the name of the dynamic libraries within the path defined in the \textit{ModuleManager}.
Finally, the chain of the components is declared within the element \textit{Chain}.
Every component inside the chain is represented by an element called \textit{Component} which has at least a \textit{name} attribute.
Its important that a plugin (*.so file found in the paths previously specified) has been loaded which provides the implementation of the component's functionality.
The further configuration of the individual web service depends on the individual component's functionality.
The \textit{Service} tag may be used to specify additional elements that the web service may then inspect.

%\task{Internet Protocol is required.}

We need to distinguish between the plugins and the components.
The plugins refer to shared libraries that can be integrated as modules with the HED to extend its functionality.
The Components refer to the implementation of web services within any of those libraries.
A \textit{Chain} will determine the path that an event takes to be noticed.
The first component of the chain is the \textit{tcp.service}.
As to be seen, the port 60000 is assigned to the server to listen to.
The port can be an arbitrary number.
However, the number 60000 is commonly used for a HED providing the A-REX web service (the one organising the computation on a site) and the number 50000 is found commonly used for a HED running web services for storage.
This way, one can organise a single server to offer multiple HED instances.
The stream which is received by this component is passed to the component defined by the \textit{next} tag.
In the present case, it will be passed to the component with the \textit{id} attribute named \textit{http}.
In this way, the message is be passed to higher layers until it reaches the \textit{Plexer}.
Depending on the path of the URL which was demanded by the HTTP, the Plexer multiplexes the request to the right web service, the right function to execute according to the component IDs and plugin names. The plexer will thus allow to have multiple web service listen to the same port.
The path, declared within the \textit{next} element, corresponds to a regular expression and leads to the service with the id named \textit{echo}. 
Hence, the service will now be reachable under URL \textit{http://localhost:60000/echo}.
It will finally process the message and create a new message which will be returned all the way back to the TCP component.
The Echo Web Service itself is provided by the ARC package.
Additional invariant parameters are passed by the elements \textit{prefix} and \textit{suffix}.
They set the characters which will enclose the echoed string.
\task{The images of the HED structure always are ordered like: TCP - TLS - HTTP - PLEXER - SOAP - WEB SERVICE   but the source code examples are: TCP - TLS - HTTP - SOAP - PLEXER - WEB SERVICE}

To create the daemon corresponding to the defined HED configuration file, ARC provides the program called \textit{arched}.
The manner of invokation is to been seen in Listing~\ref{lst:arcecho_arched_invokation}.
\lstsetKSH
\begin{lstlisting}[
label=lst:arcecho_arched_invokation,float,
caption={[Invokation of the Arched Daemon.]
         \textbf{Invokation of the Arched Daemon.\textcolor{white}{hmf}}}]

@@

In this example, the server and the client are running on the same computer such that the hostname \textit{localhost} can be utilized. 
For debugging it is advisable to check the logfile which was assigned inside the HED configuration file.
It is commonly found at /var/log/arched.log

The following chapters explain how to develop custom web services.
The first one will be the simple Time Web Service.

>>>>

This document gently introduces to preparation of standalone webservices and cognate clients with the Advance Resource Connector (ARC).
The reader is guided through a series of the practically oriented examples.
Each are accompanied by explanations of the main concepts of the software architecture.
No particular skills are required to follow the presented steps.
It is however beneficial to have some basic comprehension of the programming language C++, the file format XML and any regular UNIX shell.
To start, the user shall have an installation of ARC-1, as it is performed with current RPM or .deb packages\footnote{see http://wiki.nordugrid.org for explicit instructions for setup}.

@@

In general, the implementation of a client is easier than the implementation of the server. 
ARC is designed as a middleware which encapsulates typical challenges of server-client infrastructures (security, exception handling, extensibility) and abstracts from the underlying computer architecture (heterogeneity of computers, computer location, protocols).
The core of ARC is the prior mentioned HED (Hosting Environment Daemon).
To the administrator HED is mostly visible as the single binary that is started and configured by a file that describes services that shall be prepared by HED.
Conceptionally, the HED determines how services shall be organised both as a principle, and for any given ARC-run server.
HED determines the very explicit presence or absence of a service at a particular address. Its many configurable layers are described later in this tutorial. 
%
At the time of writing, the endpoint of the HED will be a SOAP based webservice.
SOAP is a long established XML-based standard for Web Service communication.
ARC abstracts from this format, but nevertheless it is useful to be aware of
the underlying message transport mechanism.

@@

The HED which was already mentioned in the section above is an essential part of the ARC middleware. 
Its task is to provide the hosting of various services at the application level and is based on the idea modularity.% allows its dynamic extension.
The HED consists of compononents called Message Chain Components (MCC), services and several modules, which shall aid the programmer to simplify the development of the Web Services: Config, Loader, Logging, XMLNode.
The MCCs are ordered within a layered structure. 
Each MCC provides a certain functionality such as communication between two applications (MCC TCP), secure data transfer (MCC TLS) or client-server architecture (MCC HTTP).
Figure~\ref{fig:HED_internal} illustrates a typical setup of a server-sided HED.

\begin{figure}[htb]
	\centering
	\includegraphics[width=14cm]{tex_introduction/HED.pdf}
	\mycaption{Example of HED structure with an Arex service and a file service.\task{ Replace image by an easier one!} }{\task{Write more stuff}\task{The images of the HED structure always are ordered like: TCP - TLS - HTTP - PLEXER - SOAP - Web Service   but the source code examples are: TCP - TLS - HTTP - SOAP - PLEXER - Web Service}}
\label{fig:HED_internal}
\end{figure}

As to be seen, the MCCs are connected which each other and passing incoming and outgoing message to the upper or the respective lower layer. In case of outgoing messages a MCC is wrapping the data of the upper layer as a payload into their own protocol (while incomming message will be unwrapped).
The lowest layer has to be a transport protocol like TCP which enables the transmission between the two applications.
Tehchnically there even lower layers required needed for the communication but they are realised within the operating system and the  network card
TCP is well suited for the application because it provides a reliable and ordered delivery of a byte stream.
Above the TCP layer is the Hypertext Transfer Protocol (HTTP). 
In case a security layer is desired (i.e. for authentication), the TLS (Transport Layer Security formerly known as SSL, Secure Sockets Layer) has to be inserted between the TCP and HTTP layers.
The HTTP provides the client-server architecture. It is stateless but offers several extensions for requests, header information and status codes. Furthermore HTTP enables the usage of Uniform Resource Locators (URL) which is used by ARC to multiplex between different services. The multiplexing layer can also be defined within the HED and is called Plexer.
Depending on the path of the URL the Plexer passes messages to a defined SOAP service which again passes the message to the Web Service~\cite{QIANG_2005}. \task{Add text here}\\
%In my understanding (because plexer is not my initial idea), plexer (as a sort of hub) can be put at both after http or soap. If you put after soap,then you are doing switching for different web services. While I put it after http, because somehow, I need to switch the message after http-processing, in more detail, one branch for soap and then web service/s, one branch for a non-soap service/server (the SP Service is not a service based on SOAP, actually it is based on http, so it is kind of web application).

The structure of the HED can be configured freely by modifying the server configuration file.
A first impression how the HED can be configured shall be given in the following example which corresponds to the HED shown in figure~\ref{fig:HED_internal}.
It uses the ARC echo service that is shipped for testing purposes with the ARC source code.

@@

The first example shall give a basic understanding in how to configure the HED for setting up a novel service.
Here, the task is to setup the regular ARC Echo Web Service.
On the command line, all that needs to be done is to invoking the \textit{arched}%
\footnote{\task{refer to the appendix in which the documentation to arc-hed is specified}}
daemon with a fitting server configuration file.
Such a fitting server configuration file is shown in Listing~\ref{lst:arched_arcecho_xml}.
It is written in XML and its structure is based on within the xsd-schema \textcolor{urgent}{URL?} .

@@

\lstinputlisting
	[
	label=lst:arched_arcecho_xml,float,
	caption={[HED configuration. Filename: arcecho\_no\_ssl.xml]
	\textbf{HED configuration. Filename: arcecho\_no\_ssl.xml\textcolor{white}{hmf}}}
	]
{../src/services/arched_arcecho.xml}
The first line of the XML file contains the XML declaration.
Several attributes can be defined here but at least the XML version should be specified.
The configuration as a whole is encapsulated by the element \textit{ArcConfig}. It also performs the setting of namespace abbreviations, which are expected to be mostly invariant across all server installations.% ABBREVIATIONS?? - MG
The \textit{Server} element, to be found at line~\ref{lst_code:arched_arcecho_Server}, provides basic settings for the daemon such as location of the Pid-file or the Log-file.
The \textit{ModuleManager} holds the path to the plugin libraries.
Several paths may be defined here.
Due to the fact that the first library fitting to the plugin name is loaded, the order is relevant.
The path should be at least assigned to the ARC installation directory.
Otherwise, the standard set of MCC modules might not be found.
The next set of elements are holding the name of the plugins to be loaded (line~\ref{lst_code:arched_arcecho_Plugins}).
The names have to correspond to the name of the dynamic libraries within the path defined in the \textit{ModuleManager}.
Finally, the chain is declared within the element \textit{Chain} which creates the layered structure.
It is composed out of the elements \textit{Component}, \textit{Plexer} and \textit{Service}.
Every element inside has at least a \textit{name} attribute.
Regarding the components and the services a plugin (*.so file found in the paths previously specified) has to be loaded which provides the implementation of its functionality. The further configuration depends on the individual functionality.\\
%
% within the chain ... 3 types of elements
%
%Its needed to distinguish between the plugins and the components.
%The plugins refer to shared libraries that can be integrated as modules with the HED to extend its functionality.
%The Components refer to the implementation of Web Services within any of those libraries.
%
%
A \textit{Chain} will determine the path that an event takes to be noticed.
The first component of the chain is the \textit{tcp.service}.
As to be seen, the port 60000 is assigned to the server to listen to.
The port can be an arbitrary number.
However, the number 60000 is commonly used for a HED providing the A-REX Web Service (the one organising the computation on a site) and the number 50000 is found commonly used for a HED running Web Services for storage.
This way, one can organise a single server to offer multiple HED instances.
The stream which is received by this component is passed to the component defined by the \textit{next} attribute.
In the present case, it will be passed to the component with the \textit{id} attribute named \textit{http}.
In this way, the message is be passed to higher layers until it reaches the \textit{Plexer}.
Depending on the path of the URL which was demanded by the HTTP, the Plexer multiplexes the request to the right Web Service, the right function to execute according to the component IDs and plugin names. The plexer will thus allow to have multiple Web Service listen to the same port.
The path, declared within the \textit{next} attribute, corresponds to a regular expression and leads to the service with the id named \textit{echo}. 
Hence, the service will now be reachable under URL \textit{http://localhost:60000/echo}.
It will finally process the message and create a new message which will be returned all the way back to the TCP component.
The Echo Web Service itself is provided by the ARC package.
Additional invariant parameters are passed by the elements \textit{prefix} and \textit{suffix}.
They set the characters which will enclose the echoed string.
\task{The images of the HED structure always are ordered like: TCP - TLS - HTTP - PLEXER - SOAP - Web Service   but the source code examples are: TCP - TLS - HTTP - SOAP - PLEXER - Web Service}

To create the daemon corresponding to the defined server configuration file, ARC provides the program called \textit{arched}.
The manner of invokation is to been seen in Listing~\ref{lst:arcecho_arched_invokation}.
\lstsetKSH
\begin{lstlisting}[
label=lst:arcecho_arched_invokation,float,
caption={[Invokation of the Arched Daemon.]
         \textbf{Invokation of the Arched Daemon.\textcolor{white}{hmf}}}]

@@

In this example, the server and the client are running on the same computer such that the hostname \textit{localhost} can be utilized. 
For debugging it is advisable to check the logfile which was assigned inside the server configuration file.
It is commonly found at /var/log/arched.log

The following chapters explain how to develop custom Web Services.
The first one will be the simple Time Web Service.
